04_DESeq_sexes

### 2019-08-28 analysis/04_DESeq2_sexes.Rmd
move theme to theme

```{r pca}
theme_set(theme_classic())

hypPCA <- returnPCAs2(vsd.hyp)
plotPC12(hypPCA, "Hypothalamus")

@@

gonPCA <- returnPCAs2(vsd.gon)
plotPC12(gonPCA, "Gonad")

@@

```{r LDA}
theme_set(theme_classic())

LDAanalysis <- function(mydds, mycolData, mysubtitle){
  # data prep
  vsd <- vst(mydds, blind=FALSE) # variance stabilized 
  tvsd <- as.data.frame(t(assay(vsd)))   # get vsd counts and transform

>>>>

```{r pca}
hypPCA <- returnPCAs2(vsd.hyp)
plotPC12(hypPCA, "Hypothalamus")

@@

gonPCA <- returnPCAs2(vsd.gon)
plotPC12(gonPCA, "Gonad")
```

@@

```{r LDA}
LDAanalysis <- function(mydds, mycolData, mysubtitle){
  # data prep
  vsd <- vst(mydds, blind=FALSE) # variance stabilized 
  tvsd <- as.data.frame(t(assay(vsd)))   # get vsd counts and transform
